\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-10-21 bare_conf.tex
text updates integrating feedback from Darius, 2nd iteration. Original feedback is available in bare_conf_Darius_feedback.pdf. bare_conf_Darius_feedback_integrated.pdf shows which comments are not yet integrated, integrated comments are removed from this pdf

Following the principles of the participatory design \cite{Kensing}, \cite{Carroll} we included the end-users into the design process of the system. Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution. During the six discussion sessions major attention was paid to:
\begin{enumerate}
\item Functionality and key features of the solution addressing real-life scenarios of visually impaired persons;
\item Technical feasibility, connecting user needs to the latest development in computer vision and assistive technologies;
\item Interface between the visually impaired person and the assistive technology;
\item Appearance, usability and potential costs of the proposed product. 
\end{enumerate}
Participatory design process included testing of assistive technologies for the blind and visually impaired people using widely available mobile phone apps like Seeing AI, BlindWays, Be my eyes, Aipoly Vision, TapTapSee, etc.
%Design process included testing of the existing mobile phone apps (Seeing AI, BlindWays, Be My Eyes, Aipoly Vision, TapTapSee) for assisting visually impaired people. 
Semi-structured tests were performed by visually impaired participants and researchers from the project group. Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.

%Darius
To have an overview of research progress on assistive technologies for the blind in the last ten years, a systematic literature review three major research databases (Medline, IEEE xplore and ACM DL) was conducted. 
we carried out  systemic review of research articles in databases like  Medline, IEEE xplore, ACM DL.  It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project). 
Systemic review of the relevant patents and patent applications worldwide was performed using online services of the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline. It revealed several main technological trends in the area of assistive technologies for the blind persons. 
Based on the above aforementioned methodical review approaches, some our insights are presented in the Results section.

@@

% User interface
UI consists of a wearable forehead belt, integrating RGB and depth cameras, inertial measurement unit (IMU), tactile feedback device and bone conduction headphones. Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment and the system at the same time, which is essential for the visually impaired people. Some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel. For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description. More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way. USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.

@@

This paper outlined a high level architecture of a computer vision-based system, which may help to partially compensate impaired or lost human vision. The main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection and present the output of the video processing to the user through a combined audio/tactile interface.

@@

The proposed architecture is based on several assumptions, which may be characterized as limitations of the system. Technical feasibility of the solution is dependent on the availability of high bandwidth Internet connection ensuring access to high-power data processing components. Insufficient bandwidth may result in latency, which may not be tolerated by the users.

@@

Economical feasibility of the proposed solution may also be questioned. Advanced technology (high-end smartphone, depth camera, tactile feedback device, bone conduction headphones) is needed to ensure reliable functioning of the system. A combination of such components may be perceived as costly by the end users. More research is needed to demonstrate the benefits of the system in real-world scenarios.

>>>>

Following the principles of the participatory design \cite{Kensing}, \cite{Carroll} we included the end-users into the design process of the system. Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution. During the six discussion sessions major attention was paid to:
\begin{enumerate}
\item Functionality and key features of the solution addressing real-life scenarios of visually impaired persons;
\item Technical feasibility, connecting user needs to the latest development in computer vision and assistive technologies;
\item Interface between the visually impaired person and the assistive technology;
\item Appearance, usability and potential costs of the proposed product. 
\end{enumerate}
Participatory design process included testing of assistive technologies for the blind and visually impaired people using widely available mobile phone apps like Seeing AI, BlindWays, Be My Eyes, Aipoly Vision, TapTapSee, etc.
%Design process included testing of the existing mobile phone apps (Seeing AI, BlindWays, Be My Eyes, Aipoly Vision, TapTapSee) for assisting visually impaired people. 
Semi-structured tests were performed by visually impaired participants and researchers from the project group. Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.

%Andrius: If we leave this section in manuscript, we should probably have a section addressing the findings of the reviews in the Results section.
%Darius
To have an overview of research progress on assistive technologies for the blind in the last ten years, a systematic literature review in three major research databases (Medline, IEEE xplore and ACM DL) was conducted. It revealed increasing research interest in the field (84 related publications were identified, while 17 were characterized as highly relevant for this project). 
%we carried out  systemic review of research articles in databases like  Medline, IEEE xplore, ACM DL.  
Systemic review of the relevant patents and patent applications worldwide was performed using online services of the following databases: EspaceNet, GooglePatents, USPTO, PatentScope, FreePatentsOnline. It revealed several main technological trends in the area of assistive technologies for the blind persons. 
Based on the aforementioned methodical reviews, some our insights are presented in the Results section.

@@

% User interface
UI consists of a wearable forehead belt, integrating RGB and depth cameras, inertial measurement unit (IMU), tactile feedback device and bone conduction headphones. Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment and the system at the same time, which is essential for the visually impaired people.

However, some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel. For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description. More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way. USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.

@@

This paper outlined a high-level architecture of a computer vision-based system, which may help to partially compensate impaired or lost human vision. The main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection and present the output of the video processing to the user through a combined audio/tactile interface.

@@

The proposed architecture is based on several assumptions, which may be characterized as limitations of the system. For instance, technical feasibility of the solution is dependent on the availability of high bandwidth Internet connection ensuring access to high-power data processing components. Insufficient bandwidth may result in latency, which may not be tolerated by the users.

@@

Economical feasibility of the proposed solution may also be questioned. Advanced technology (high-end smartphone, depth camera, tactile feedback device, bone conduction headphones) is needed to ensure reliable functioning of the system. A combination of such components may be perceived as costly by the end users. More research is needed to demonstrate the cost-benefit analysis of the system in real-world scenarios.
